\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-11-08 paper/manuscript.tex
hierarchical clustering, improved stm table, some other things

\author{ Markus Neumann \and Bruce Desmarais \and Hanna Wallach} \date{\today}

@@

%fightin words results
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Top democratic and Republican words (Indiana), according to the informed Dirichlet model of Monroe et al. (2008).}
	\label{fightinwords}
	\includegraphics[width=\linewidth]{figures/fightinWords.png}
\end{figure}

%fightin words results
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Top democratic and Republican words (Louisiana), according to the informed Dirichlet model of Monroe et al. (2008).}
	\label{fightinwordsLA}
	\includegraphics[width=\linewidth]{figures/fightinWordsLA.png}
\end{figure}

%Partisan top words - topic model
\input{tables/partisanTopWords.tex}

%Partisan top words - fightin words
\input{tables/fightinwords.tex}

%Partisan top words - topic model
\input{tables/partisanTopWordsLA.tex}

%Partisan top words - fightin words
\input{tables/fightinwordsLA.tex}

%HOW TO DO THIS???
%\begin{table}
%	\input{tables/fightinwords.tex}
%\end{table}

%Some basic descriptive statistics of documents by party
\input{tables/descriptiveStatisticsPartisan.tex}

>>>>

\author{ Markus Neumann \and Bruce Desmarais \and Hanna Wallach \and Fridolin Linder} \date{\today}

@@

%fightin words results
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Top democratic and Republican words (Indiana), according to the informed Dirichlet model of Monroe et al. (2008). Ordering is top to bottom for Democrats, and vice versa for Republicans.}
	\label{fightinwords}
	\includegraphics[width=\linewidth]{figures/fightinWords.png}
\end{figure}

%fightin words results
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Top democratic and Republican words (Louisiana), according to the informed Dirichlet model of Monroe et al. (2008). Ordering is top to bottom for Democrats, and vice versa for Republicans.}
	\label{fightinwordsLA}
	\includegraphics[width=\linewidth]{figures/fightinWordsLA.png}
\end{figure}

%Partisan top words - topic model Indiana
\input{tables/partisanTopWords.tex} %\ref{tabFightinIN}

%Partisan top words - topic model Louisiana
\input{tables/partisanTopWordsLA.tex} %tabLDALA

%Partisan top words - fightin words Indiana
\input{tables/fightinwordsIN.tex} %\ref{tabFightinIN}

%Partisan top words - fightin words Louisiana
\input{tables/fightinwordsLA.tex} %\ref{tabFightinLA}

%Partisan top words - stm Indiana
\input{tables/stmTopWordsIN.tex} %\ref{tabSTMLA}

%Partisan top words - stm Louisiana
\input{tables/stmTopWordsLA.tex} %\ref{tabSTMLA}

%Some basic descriptive statistics of documents by party
\input{tables/descriptiveStatisticsPartisanIN.tex}

%Some basic descriptive statistics of documents by party
\input{tables/descriptiveStatisticsPartisanLA.tex}

%fightin words results
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Total number of lines retained at a given threshold for removing duplicated lines. For example, at x = 10, all lines occurring more than 10 times within a city's documents are removed.}
	\label{linesCutoff}
	\includegraphics[width=\linewidth]{figures/linesCutoffIN.pdf}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Hierarchical clustering (Indiana).}
	\label{hclustIN}
	\includegraphics[width=\linewidth]{figures/clusteringIN.png}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Hierarchical clustering (Louisiana).}
	\label{hclustLA}
	\includegraphics[width=\linewidth]{figures/clusteringLA.png}
\end{figure}
